Deriving Multi-headed Planar Dependency Parses from Link Grammar Parses

### 2014-05-20 doc/LinksToDAG.tex
note for discussion

>>>>

We should acknowledge that another option would be to post-process either CoNLL parses or our link parses to automatically add more multi-heading, e.g., to handle control phenomena ("John wants to skip" or "Jane ran for office in order to change the tax laws" should have John/Jane be the subject of two verbs).  However, that requires per-language
